Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-11 paper/paper.tex
Punctuation

We demonstrate the effectiveness of our method by synthesizing several subtle
programs acting on machine integers, and a selection of floating-point programs.
\end{abstract}

@@

\begin{figure}
\begin{center}
{\tiny
\include{figures/results_table}
}
\end{center}
\caption{Time for synthesis of machine integer benchmarks from~\cite{brahma}
 \label{fig:results-table}}
\end{figure}

\begin{figure}
\begin{center}
{\tiny
\include{figures/icse_results_table}
}
\end{center}
\caption{Times for synthesis of machine integer benchmarks from~\cite{brahma-icse}}
\label{fig:icse-results-table}
\end{figure}

>>>>

We demonstrate the effectiveness of our method by synthesizing several subtle
programs acting on machine integers, and a previously un-synthesised floating-point program.
\end{abstract}

@@

\begin{figure}
\begin{center}
{\tiny
\include{figures/results_table}
}
\end{center}
\caption{Time for synthesis of machine integer benchmarks from~\cite{brahma}.
 \label{fig:results-table}}
\end{figure}

\begin{figure}
\begin{center}
{\tiny
\include{figures/icse_results_table}
}
\end{center}
\caption{Times for synthesis of machine integer benchmarks from~\cite{brahma-icse}.}
\label{fig:icse-results-table}
\end{figure}
